A formal approach but practical approach in train regulation

### 2025-06-19 paper/main.tex
Clarification trackworks

We suppose that the train network can be described as follows. First, we consider given a set of blocks: $\blocks = \{ 1, 2, \ldots, n\}$. Blocks are oriented: there is a $\dirForward$ end and a $\dirBackward$ one. Let $\directions = \{\dirForward, \dirBackward\}$ be the set of directions.  Next, we suppose given a set $\turnouts = \{ n+1, \ldots, m\}$, the identifiers  of trackworks (switches, crossings, double slip switches, and so on\todo{Est-ce que ces élements sont dans le modèle de Lucas, en particulier les crossings et double slip switches ?}). Trackworks are characterized by an internal state: switches can be in direct or deviate position (next denoted '\direct' and '\deviate'), a crossing has only one internal position, a double slip switch can be straight through or crossing. In the examples, to simplify the presentation, we use only switches, but our model is not restricted to them.  Let $\internalState$ denotes the set of internal states. A \emph{network configuration} is given by a function $\sigma: \turnouts \to \internalState$. Let $\networkConf$ denotes the set of all network configurations. For two turnouts $\theta = \{9, 10\}$, the function $9 \mapsto \deviate, 10 \mapsto \direct$ states that $9$ is in deviate position while 10 is in direct one. The latter function is also described via an array  $[\deviate, \direct]$ giving states in trackwork order.

>>>>

We suppose that the train network can be described as follows. First, we consider given a set of blocks: $\blocks = \{ 1, 2, \ldots, n\}$. Blocks are oriented: there is a $\dirForward$ end and a $\dirBackward$ one. Let $\directions = \{\dirForward, \dirBackward\}$ be the set of directions.  Next, we suppose given a set $\turnouts = \{ n+1, \ldots, m\}$, the identifiers  of trackworks\footnote{For the sake of simplicity, in this paper, we only consider switches. Our work can easily be extended to crossings and double slip switches.}. Trackworks are characterized by an internal state: switches can be in direct or deviate position (next denoted '\direct' and '\deviate'), a crossing has only one internal position, a double slip switch can be straight through or crossing. In the examples, to simplify the presentation, we use only switches, but our model is not restricted to them.  Let $\internalState$ denotes the set of internal states. A \emph{network configuration} is given by a function $\sigma: \turnouts \to \internalState$. Let $\networkConf$ denotes the set of all network configurations. For two turnouts $\theta = \{9, 10\}$, the function $9 \mapsto \deviate, 10 \mapsto \direct$ states that $9$ is in deviate position while 10 is in direct one. The latter function is also described via an array  $[\deviate, \direct]$ giving states in trackwork order.
